Data preparation

### 2024-04-08 analysis/supplementary_materials/data preparation.qmd
implementation of changed gao data

```{r}
Gao <- read_csv2(here::here("analysis/data/raw_data/Gao.csv")) |> rename("dragged_comb" = "Comb_tot",
    "channel" = "Channel_comb",
          "folded_strip_roulette" = "Folded strip roulette",
"twisted_cord_roulette" = "Twisted twine",
"paint" = "Paint_total", #translation unsure
"unidentified_roulette" = "Unident. Twine",
"cord_wrapped_roulette" = "Sisal", # Cisse (2011, 161) identifies them as cord_wrapped_roulette after Nixon (2008, 183)
"straight_mat_impression" = "Birdfood" # Cisse (2011, 161) identified it as mat, but not completly sure, maybe other mat than straight
) |> 
mutate_if(is.numeric, round, digits=0) #rounding the numbers (because they were extracted from graphics there were minor deviations)

@@

Gao9_decor <- Gao |> 
  filter(Phase == "lower") |> 
  select(-"Site-Code", -"Phase", -"n_gao") |> 
  mutate(Site = "Gao9") |> 
  column_to_rownames("Site")

@@

names(Gao)

n_gao <- data.frame(
  site = c("Gao12", "Gao9"),
  n = c(n_gao)
)
```

>>>>

```{r}
Gao <- read_csv2(here::here("analysis/data/raw_data/Gao.csv")) |> rename("dragged_comb" = "Comb_tot",
    "channel" = "Channel_comb",
          "folded_strip_roulette" = "Folded strip roulette",
"twisted_cord_roulette" = "Twisted twine",
"paint" = "Paint_total", #translation unsure
"unidentified_roulette" = "Unident. Twine",
"cord_wrapped_roulette" = "Sisal", # Cisse (2011, 161) identifies them as cord_wrapped_roulette after Nixon (2008, 183)
"straight_mat_impression" = "Birdfood" # Cisse (2011, 161) identified it as mat, but not completly sure, maybe other mat than straight
) |> 
  filter(Phase != "lower") |> 
  mutate(Site = "Gao") |> 
mutate_if(is.numeric, round, digits=0) #rounding the numbers (because they were extracted from graphics there were minor deviations)

Gao <- as.data.frame(Gao)

@@

Gao9_decor <- Gao |> 
  filter(Phase == "upper") |> 
  select(-"Site-Code", -"Phase") |> 
  mutate(Site = "Gao9") |> 
  column_to_rownames("Site") |> 
  select(-"n_gao")

@@

n_gao <- data.frame(
  site = c("Gao12", "Gao9"),
  n = c(n_gao)
)

Gao
```
